### 2014-05-21 sprout_related.tex
Import Remy
Lowercase section headings
Fix references

\section{Related Work}
\label{s:related}

@@

Traditional congestion-control algorithms generally do not
simultaneously achieve high utilization and low delay over paths with
high rate variations.
%They also often introduce long and variable
%delays.
Early TCP variants such as Tahoe and Reno~\cite{Jacobson88} do not
explicitly adapt to delay (other than from ACK clocking), and require
an appropriate buffer size for good performance. TCP
Vegas~\cite{Brakmo94}, FAST~\cite{FAST}, and Compound TCP~\cite{CTCP}
incorporate round-trip delay explicitly, but the adaptation is
reactive and does not directly involve the receiver's observed rate.

LEDBAT~\cite{ledbat} (and TCP Nice~\cite{tcpnice}) share our goals of
high throughput without introducing long delays, but LEDBAT does not
perform as well as Sprout. We believe this is because of its choice of
congestion signal (one-way delay) and the absence of forecasting.
Some recent work proposes TCP receiver modifications to combat
bufferbloat in 3G/4G wireless networks~\cite{tcpbufferbloat}.
%We note
%that it is not enough to reactively throttle the receiver window when
%delays rise, because one needs mechanisms to predict rate increases
%and outages as well.
Schemes such as ``TCP-friendly'' equation-based
rate control~\cite{ebcc} and binomial congestion
control~\cite{binomial} exhibit slower transmission rate variations
than TCP, and in principle could introduce lower delay, but perform
poorly in the face of sudden rate changes~\cite{slowcc-dynamic}.

>>>>

\section{Related work}
\label{sprout:related}

@@

Traditional congestion-control algorithms generally do not
simultaneously achieve high utilization and low delay over paths with
high rate variations.
%They also often introduce long and variable
%delays.
Early TCP variants such as Tahoe and Reno~\cite{Jacobson88} do not
explicitly adapt to delay (other than from ACK clocking), and require
an appropriate buffer size for good performance. TCP
Vegas~\cite{vegas}, FAST~\cite{fasttcp}, and Compound TCP~\cite{compound}
incorporate round-trip delay explicitly, but the adaptation is
reactive and does not directly involve the receiver's observed rate.

LEDBAT~\cite{ledbat} (and TCP Nice~\cite{tcpnice}) share our goals of
high throughput without introducing long delays, but LEDBAT does not
perform as well as Sprout. We believe this is because of its choice of
congestion signal (one-way delay) and the absence of forecasting.
Some recent work proposes TCP receiver modifications to combat
bufferbloat in 3G/4G wireless networks~\cite{tcpbufferbloat}.
%We note
%that it is not enough to reactively throttle the receiver window when
%delays rise, because one needs mechanisms to predict rate increases
%and outages as well.
Schemes such as ``TCP-friendly'' equation-based
rate control~\cite{ebcc} and binomial congestion
control~\cite{binomial} exhibit slower transmission rate variations
than TCP, and in principle could introduce lower delay, but perform
poorly in the face of sudden rate changes~\cite{slowcc}.
